---
title: "Photosynthesis TPC fitting"
authors: Hollie Putnam 
edited by: Hollie Putnam 
date: 20230327
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library('rTPC')
library('nls.multstart')
library(tidyverse)
library(broom)
```

## Import data
```{r, warning = FALSE}
Photodata <- read.csv("data/TPC/Dec_Photo_Rawextracted_rates.csv")
Photodata <- Photodata %>%
  filter(Temp.Cat!=25)
# Try May photodata?
#Photodata <- read.csv("~/Downloads/May_Photo_extracted_rates.csv")
```

TPC fitting 
Padifeld et al **rTPC and nls.multstart: A new pipeline to fit thermal performance curves in r**  
https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.13585  

Sharpe Schoolfield 1981 model
Schoolfield, R. M., Sharpe, P. J. H., & Magnuson, C. E. (1981). Non-linear regression of biological temperature-dependent rate models based on absolute reaction-rate theory. Journal of theoretical biology, 88(4), 719-731. https://doi.org/10.1016/0022-5193(81)90246-0

```{r}
#Respiration
Photodata$temp <- as.numeric(Photodata$Temp.Cat)
Photodata$transformed.rate <- log10(Photodata$micromol.cm2.h+1)

# choose model
get_model_names()
#sharpeschoolhigh_1981

# get start vals
start_vals <- get_start_vals(Photodata$temp,Photodata$transformed.rate, model_name = 'sharpeschoolhigh_1981')
start_vals[2] <- 0.01

# get limits
low_lims <- get_lower_lims(Photodata$temp,Photodata$transformed.rate, model_name = 'sharpeschoolhigh_1981')
upper_lims <- get_upper_lims(Photodata$temp,Photodata$transformed.rate, model_name = 'sharpeschoolhigh_1981')

#view values
start_vals
low_lims
upper_lims
```

#individal fitting
```{r}

# fit  chosen model formulation in rTPC
d_fits <- Photodata %>% group_by(fragment_ID) %>% nest() %>%
  mutate(sharpeschoolhigh = map(data, ~nls_multstart(transformed.rate~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28),
                        data = .x,
                        iter = c(3,3,3,3),
                        start_lower = start_vals - 1,
                        start_upper = start_vals + 1,
                        lower = low_lims,
                        upper = upper_lims,
                        supp_errors = 'Y',
                        convergence_count = FALSE)))


```

```{r}
# create new list column of for high resolution data
d_preds <- mutate(d_fits, new_data = map(data, ~tibble(temp = seq(min(.x$temp), max(.x$temp), length.out = 50)))) %>%
  # get rid of original data column
  select(., -data) %>%
  # stack models into a single column, with an id column for model_name
  pivot_longer(., names_to = 'model_name', values_to = 'fit', sharpeschoolhigh) %>%
  # create new list column containing the predictions
  # this uses both fit and new_data list columns
  mutate(preds = map2(fit, new_data, ~augment(.x, new_data = .y))) %>%
  # select only the columns we want to keep
  select(fragment_ID, preds) %>%
  # unlist the preds list column
  unnest(preds)

glimpse(d_preds)
```


```{r}

ggplot(d_preds) +
  geom_line(aes(Temp.Cat, .fitted)) +
  geom_point(aes(Temp.Cat, transformed.rate), mutate(Photodata, fragment_ID = fragment_ID)) +
  facet_wrap(~fragment_ID, ncol = 6) +
  theme_bw() +
  theme(legend.position = 'none') +
  scale_color_brewer(type = 'qual', palette = 2) +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'All fitted thermal performance curves',
       subtitle = 'sharpeschoolhigh in orange')


```

```{r}
d_params1 <- pivot_longer(d_fits, names_to = 'model_name', values_to = 'fit', sharpeschoolhigh) %>%
  mutate(params = map(fit, calc_params),
         rss = map_dbl(fit, deviance)) 
d_params1 %>% arrange(rss)

#### Filter Topt data based on quality of fit?
d_params <- d_params1 %>%
  #filter(rss < 0.01) %>%
  select(fragment_ID, rss, params) %>%
  unnest(params)

glimpse(d_params)

d_params
write_csv(d_params, path = "data/processed/TPC_Dec_Photo_params_ind_without25.csv")
```


# Fit TPCs to haplotype groups instead of individual corals
```{r}
# fit  chosen model formulation in rTPC
d_fits_groups <- Photodata %>% group_by(mtORF) %>% nest() %>%
  mutate(sharpeschoolhigh = map(data, ~nls_multstart(transformed.rate~sharpeschoolhigh_1981(temp = Temp.Cat, r_tref,e,eh,th, tref = 28),
                        data = .x,
                        iter = c(3,3,3,3),
                        start_lower = start_vals - 1,
                        start_upper = start_vals + 1,
                        lower = low_lims,
                        upper = upper_lims,
                        supp_errors = 'Y',
                        convergence_count = FALSE)))

d_preds_groups <- mutate(d_fits_groups, new_data = map(data, ~tibble(temp = seq(min(.x$temp), max(.x$temp), length.out = 50)))) %>%
  # get rid of original data column
  select(., -data) %>%
  # stack models into a single column, with an id column for model_name
  pivot_longer(., names_to = 'model_name', values_to = 'fit', sharpeschoolhigh) %>%
  # create new list column containing the predictions
  # this uses both fit and new_data list columns
  mutate(preds = map2(fit, new_data, ~augment(.x, new_data = .y))) %>%
  # select only the columns we want to keep
  select(mtORF, preds) %>%
  # unlist the preds list column
  unnest(preds)

glimpse(d_preds_groups)
d_preds_groups

ggplot(d_preds_groups) +
  geom_line(aes(Temp.Cat, .fitted)) +
  geom_point(aes(Temp.Cat, transformed.rate), Photodata) +
  facet_wrap(~mtORF) +
  theme_bw() +
  theme(legend.position = 'none') +
  scale_color_brewer(type = 'qual', palette = 2) +
  labs(x = 'Temperature (ºC)',
       y = 'Metabolic rate',
       title = 'All fitted thermal performance curves',
       subtitle = 'sharpeschoolhigh in orange')

d_params_groups <- pivot_longer(d_fits_groups, names_to = 'model_name', values_to = 'fit', sharpeschoolhigh) %>%
  mutate(params = map(fit, calc_params)) %>%
  select(mtORF, params) %>%
  unnest(params)

glimpse(d_params_groups)

d_params_groups
write_csv(d_params_groups, path = "data/processed/TPC_params_grp.csv")
```

